Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-03-02 paper.tex
updated authors
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{Lucas C. Cordeiro \\
Department of Computer Science\\
University of Oxford, UK\\
Email: lucas.cordeiro@cs.ox.ac.uk
\and
Eddie B. de Lima Filho \\
Science, Technology, and Innovation Center\\ for the Industrial Pole of Manaus, Brazil \\
Email: eddie@ctpim.org.br}
%\IEEEauthorblockN{Homer Simpson}
%\IEEEauthorblockA{Twentieth Century Fox\\
%Springfield, USA\\
%Email: homer@thesimpsons.com}
%\and
%\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
%\IEEEauthorblockA{Starfleet Academy\\
%San Francisco, California 96678--2391\\
%Telephone: (800) 555--1212\\
%Fax: (888) 555--1212}}

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{Lucas C. Cordeiro \\
%Department of Computer Science\\
University of Oxford, UK\\
lucas.cordeiro@cs.ox.ac.uk
\and
Eddie B. de Lima Filho \\
Samsung Electronics, Brazil \\
eddie.l@samsung.com
\and
Iury V. de Bessa \\
Federal University of Amazonas, Brazil \\
iury.bessa@ufam.edu.br}
%\IEEEauthorblockN{Homer Simpson}
%\IEEEauthorblockA{Twentieth Century Fox\\
%Springfield, USA\\
%Email: homer@thesimpsons.com}
%\and
%\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
%\IEEEauthorblockA{Starfleet Academy\\
%San Francisco, California 96678--2391\\
%Telephone: (800) 555--1212\\
%Fax: (888) 555--1212}}
